Closer look at DDM parameter estimates

### 2017-05-02 DDM_Report.Rmd
added pre post refitting differences

Summary of absolute difference in parameter estimates

@@

all_hddm %>%
  gather(key, value, -sub_id, -pre_post) %>%
  arrange(sub_id) %>%
  spread(pre_post, value) %>%
  mutate(abs_diff = pre-post) %>%
  group_by(key) %>%
  summarise(mean_abs_diff = mean(abs_diff, na.rm=T),
            median_abs_diff = median(abs_diff, na.rm=T),
            min_abs_diff = min(abs_diff, na.rm=T),
            max_abs_diff = max(abs_diff, na.rm=T),
            sd_abs_diff = sd(abs_diff, na.rm=T))
```

How to reliabilities change w sample size (refit from 50 to 150) both for EZ and hddm (gives a prescriptive recommendation on which method to use depending on sample size)

>>>>

Summary of absolute difference in parameter estimates.

**GO ON SHERLOCK AND CHECK IF YOU INDEED FIT IT TO THE RETEST SAMPLE ONLY**

@@

all_hddm %>%
  gather(key, value, -sub_id, -pre_post) %>%
  arrange(sub_id) %>%
  spread(pre_post, value) %>%
  mutate(abs_diff = pre-post) %>%
  group_by(key) %>%
  summarise(mean_abs_diff = mean(abs_diff, na.rm=T),
            median_abs_diff = median(abs_diff, na.rm=T),
            min_abs_diff = min(abs_diff, na.rm=T),
            max_abs_diff = max(abs_diff, na.rm=T),
            sem_abs_diff = sem(abs_diff)) %>%
  ggplot(aes(reorder(key, mean_abs_diff), mean_abs_diff))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_abs_diff-sem_abs_diff, ymax = mean_abs_diff+sem_abs_diff), position=position_dodge(0.9), width = 0.25)+
  theme_bw()+
  geom_hline(yintercept=0, linetype='dashed', color='red')+
  ylab("Mean absolute difference after refit")+
  xlab("")+
  coord_flip()
```

Are the variables we see the changes on different due to transformation?

```{r}
raw_pre_correction <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_subs_test_data_preddm_correction.csv')

replace_hddm_vars = data.frame(grep('hddm', names(raw_pre_correction), value=T, perl=T))
names(replace_hddm_vars) = c('var')

raw_pre_correction = raw_pre_correction[,c("sub_id", as.character(replace_hddm_vars$var))]

hddm_fix_retest_subs_test_data = raw_pre_correction

raw_hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')

for(i in 1:length(names(hddm_fix_retest_subs_test_data))){
  if(names(hddm_fix_retest_subs_test_data)[i] %in% replace_hddm_vars$var){
    hddm_fix_retest_subs_test_data[,names(hddm_fix_retest_subs_test_data)[i]] <- raw_hddm_refits[,names(hddm_fix_retest_subs_test_data)[i]]
  }
}

raw_post_correction <- hddm_fix_retest_subs_test_data

raw_pre_correction = raw_pre_correction %>% mutate(pre_post = "pre")
raw_post_correction = raw_post_correction %>% mutate(pre_post = "post")

raw_all_hddm = rbind(raw_pre_correction, raw_post_correction)

raw_all_hddm %>%
  gather(key, value, -sub_id, -pre_post) %>%
  arrange(sub_id) %>%
  spread(pre_post, value) %>%
  mutate(abs_diff = pre-post) %>%
  group_by(key) %>%
  summarise(mean_abs_diff = mean(abs_diff, na.rm=T),
            median_abs_diff = median(abs_diff, na.rm=T),
            min_abs_diff = min(abs_diff, na.rm=T),
            max_abs_diff = max(abs_diff, na.rm=T),
            sem_abs_diff = sem(abs_diff)) %>%
  ggplot(aes(reorder(key, mean_abs_diff), mean_abs_diff))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_abs_diff-sem_abs_diff, ymax = mean_abs_diff+sem_abs_diff), position=position_dodge(0.9), width = 0.25)+
  theme_bw()+
  geom_hline(yintercept=0, linetype='dashed', color='red')+
  ylab("Mean absolute difference after refit")+
  xlab("")+
  coord_flip()
```

How do reliabilities change w sample size (refit from 50 to 150) both for EZ and hddm (gives a prescriptive recommendation on which method to use depending on sample size)
